\begin{center}
  {\LARGE\bfseries rvLLM: an accelerator-oriented inference runtime\par}
  \vspace{0.5em}
  {\large m0at\par}
  {\small\texttt{https://github.com/solidsf-inc/rvLLM}\par}
\end{center}

\begin{abstract}
rvLLM is a Rust inference runtime organized around explicit memory layouts,
paged key/value state, accelerator-specific kernels, and fail-closed dispatch.
The public source contains a CUDA serving path plus experimental Metal and
vision components. This note describes the source architecture; it makes no
performance claim because no released-source benchmark receipt accompanies it.
\end{abstract}

\section{Architecture}
The \texttt{v3} workspace separates model configuration, loading, memory,
metadata, attention, fused operations, graph capture, sampling, scheduling, and
HTTP serving. The runtime owns the state transition from a validated request to
a batch plan, accelerator launches, and collected output. Accelerator-specific
artifacts are explicit inputs and missing required artifacts are errors.

\section{Execution}
Prefill creates model state and paged key/value entries for the prompt. Decode
reuses that state while advancing sequence metadata one token at a time. Each
layer applies normalization, projections, rotary position encoding, attention,
feed-forward operations, and residual updates. Final normalization, the
language-model head, and sampling select output tokens.

\section{Correctness boundaries}
Model files and metadata are untrusted inputs. Sizes and offsets require checked
arithmetic, paths must stay within configured roots, and unsupported dtypes or
shapes must fail before launch. Captured graphs are valid only for the exact
buffer layout and launch fingerprint used during capture. Performance changes
must preserve reference, eager/replay, and real-weight parity.

\section{Serving surface}
The server exposes local health, status, metrics, model listing, text completion,
and chat completion routes. It binds loopback only. Remote use requires an
audited TLS/authentication proxy. Multiple-choice generation and the Responses
API are outside the implemented surface.

\section{Status and evaluation}
CUDA is the primary integrated backend. Metal and vision code are feature-gated
and remain release-blocked until reproducible real-device, real-weight parity
and API smoke tests are published. Benchmark results require an immutable source
SHA, complete environment, raw output, and a content-hashed receipt.

\section{Licensing}
rvLLM is distributed under Apache License 2.0. Third-party ports retain upstream
notices and, where applicable, immediate-source revisions in source headers and
\texttt{LICENSES/}.
